---
# IMPORTANT: Change settings here, but DO NOT change the spacing AT ALL.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Netflix"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

Thesis_FP: FALSE

AddTitle: TRUE 
Author1: "Anya Nash"  
Ref1: "Stellenbosch University, Stellenbosch, South Africa" 
Email1: "25051911\\@sun.ac.za" 
CorrespAuthor_1: TRUE  

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- General:
RemovePreprintSubmittedTo: FALSE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
header-includes:
  - \providecommand{\pandocbounded}[1]{#1}    
---


```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

library(tidyverse)
library(here)

```



```{r, echo=FALSE}
# load data and code scripts

credits <- readRDS(here::here("data", "netflix", "credits.rds"))
netflix_movies <- read_csv(here::here("data", "netflix", "netflix_movies.csv"))
titles <- readRDS(here::here("data", "netflix", "titles.rds"))
hbo_credits <- readRDS(here::here("data", "US_Baby_names", "HBO_credits.rds"))
hbo_titles <- readRDS(here::here("data", "US_Baby_names", "HBO_titles.rds"))

```


```{r, echo=FALSE}
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```


```{r, echo=FALSE}
df_countries_long <- Countries_Long(titles)
```


## Summary of the Top 10 Netflix Content-Producing Countries

```{r, echo=FALSE}
Netflix_Country_Content_Bar(df_countries_long)
```

As seen in the graph above, the US produces by far the most content for Netflix. The next two highest countries are India and Great Britain.

## Relationship Between Movie TMDB Score and Runtime

The scatter plot below shows the relationship between TMDB score and runtime, by genre. As shown by the graph below, there is a very weak relationship between TMDB score and runtime. Interestingly, though, comedies, documentations and dramas have a somewhat similar TMDB score, but the runtime for comedies and documentations is, on average, shorter than the runtime of dramas. Romances and thrillers tend to have lower scores than the aforementioned genres.

```{r, fig.width=12, fig.height=6, out.width="100%", echo=FALSE}
Netflix_TMDB_Scatter_Movies(
  titles,
  x_var = "runtime"
)
```

## Average TMDB Popularity of movies over time by genre and country

The graphs below plot the average TMDB popularity by genre and country over time. The countries that produce the most Netflix movies are plotted (individually) and only the top 6 genres per country are included.

### US

As seen in the graph below, the top 6 genres for production in the US are: comedy, drama, romance, documentation, horror and thriller. The popularity of dramas and thrillers has increased exponentially since 2020. Therefore, it would be a good decision to focus on streaming dramas and thrillers produced in the US.

```{r, fig.width=12, fig.height=6, out.width="100%", echo=FALSE}
Plot_Movie_Genre_Popularity(
  df = titles,
  Country = "US",
  country_col = "production_countries",
  genre_col = "genres",
  year_col = "release_year",
  popularity_col = "tmdb_popularity",
  type_col = "type",
  movie_value = "MOVIE",
  top_n_genres = 6
)
```

### India

As seen in the graph below, the top 6 genres for production in India are: comedy, drama, romance, action, crime and thriller. The popularity of actions and comedies has increased exponentially since the late 2010s. Therefore, it would be a good decision to focus on streaming actions and comedies produced in India.

```{r, fig.width=12, fig.height=6, out.width="100%", echo=FALSE}
Plot_Movie_Genre_Popularity(
  df = titles,
  Country = "IN",
  country_col = "production_countries",
  genre_col = "genres",
  year_col = "release_year",
  popularity_col = "tmdb_popularity",
  type_col = "type",
  movie_value = "MOVIE",
  top_n_genres = 6
)
```

### Great Britain

As seen in the graph below, the top 6 genres for production in Great Britain are: comedy, drama, romance, action, documentation and thriller. The popularity of actions and documentations has increased slightly since 2020. Therefore, it would be a good decision to focus on streaming actions and documentations produced in Great Britain. I would be hesitant to focus on streaming thrillers from Great Britain because, despite increasing exponentially in 2020, their popularity appears to be on a heavy downward trend, so it woud be a riskier investment.

```{r, fig.width=12, fig.height=6, out.width="100%", echo=FALSE}
Plot_Movie_Genre_Popularity(
  df = titles,
  Country = "GB",
  country_col = "production_countries",
  genre_col = "genres",
  year_col = "release_year",
  popularity_col = "tmdb_popularity",
  type_col = "type",
  movie_value = "MOVIE",
  top_n_genres = 6
)
```

### France

As seen in the graph below, the top 6 genres for production in France are: comedy, drama, documentation, action, crime and thriller. The popularity of thrillers and crime has increased exponentially since 2020. Therefore, it would be a good decision to focus on streaming thrillers and crime produced in France.

```{r, fig.width=12, fig.height=6, out.width="100%", echo=FALSE}
Plot_Movie_Genre_Popularity(
  df = titles,
  Country = "FR",
  country_col = "production_countries",
  genre_col = "genres",
  year_col = "release_year",
  popularity_col = "tmdb_popularity",
  type_col = "type",
  movie_value = "MOVIE",
  top_n_genres = 6
)
```

### Canada

As seen in the graph below, the top 6 genres for production in Canada are: animation, documentation, fantasy, comedy, drama and thriller. The popularity of fantasies, comedies and dramas have increased exponentially since the late 2010s. Therefore, it would be a good decision to focus on streaming fantasies, comedies and dramas produced in Canada.

```{r, fig.width=12, fig.height=6, out.width="100%", echo=FALSE}
Plot_Movie_Genre_Popularity(
  df = titles,
  Country = "CA",
  country_col = "production_countries",
  genre_col = "genres",
  year_col = "release_year",
  popularity_col = "tmdb_popularity",
  type_col = "type",
  movie_value = "MOVIE",
  top_n_genres = 6
)
```

### Overall Recommendations

Therefore, my advice would be to invest in streaming the following genres of movies produced in the following countries:

- Drama: US
- Thriller: France (and maybe the US as well)
- Comedy: India
- Action: India (and maybe Great Britain as well)
- Documentation: France
- Fantasy: Canada
- Drama: Canada

I would start off being a bit cautious of streaming movies that have the genres because there is no obvious upward trend in any of the countries analysed:

 - Animation
 - Romance
 



