---
title: "US Baby Names"

documentclass: "elsarticle"
Thesis_FP: FALSE
AddTitle: TRUE 
Author1: "Anya Nash"  
Ref1: "Stellenbosch University, Stellenbosch, South Africa" # First Author's Affiliation
Email1: "25051911\\@sun.ac.za"
# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE 
# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal
# ---------- General:
RemovePreprintSubmittedTo: FALSE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.
output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 
    fig_height: 3.5
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

library(tidyverse)
library(here)

```

```{r, echo=FALSE,}
# load data and code scripts

state_baby_names <- readRDS(here::here("data", "US_Baby_names", "Baby_Names_By_US_State.rds"))
song_charts <- readRDS(here::here("data", "US_Baby_names", "charts.rds"))
hbo_credits <- readRDS(here::here("data", "US_Baby_names", "HBO_credits.rds"))
hbo_titles <- readRDS(here::here("data", "US_Baby_names", "HBO_titles.rds"))

```

```{r, echo=FALSE,}
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```


## Spearman Correlation by Year

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
baby_names_national <- Create_National_Dataset(state_baby_names)

rank_corr_df <- Name_Rank_Correlation(baby_names_national, top_n_names = 25, max_lead = 3)
```

### Spearman Correlation for Female Names

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
Rank_Corr_Graph(rank_corr_df, "F")
```
The graph shows that the top 25 female names are very persistent for the time period analysed. For most of the years, the Spearman rank correlation is between 0.8 and 1, except for between 1960 and 1970, around 1985 and around 2005. Therefore, if a female name is in the top 25, then there is a very high probability that it will be in the top 25 in the following year as well as the year after that. According to this graph, it appears that female names are no more or less likely to persist since the 1990s compared to earlier years; the pattern does not appear to change significantly from the 1990s.

### Spearman Correlation for Male Names

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
Rank_Corr_Graph(rank_corr_df, "M")
```

The graph shows that the top 25 male names are very persistent for the time period analysed. Before 1965, the Spearman rank correlation remains between 0.85 and 1, however, the range significantly increases and the consistency decreases after 1965. This indicates that male names were initially quite persistent, but that persistence has decreased significantly since 1965. Therefore, the probability of a male name remaining in the top 25 male names began very high, but in more recent years, that probability has become smaller. From this graph, it appears that male names are less persistent since the 1990s than prior to that - popular names have become a bit slower to persist since the 1990s.

## Spearman Correlation by Decade

```{r, echo=FALSE,}
decade_corr <- Name_Decade_Rank_Correlation(
  df = baby_names_national,
  top_n_names = 25,
  max_lead_decades = 3
)
```

### Spearman Correlation by Decade for Female Names

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
Decade_Corr_Plot(decade_corr, "F")
```

The same trends are apparent when looking at popular female names by decade - according to this graph, it appears that female names are no more or less likely to persist since the 1990s compared to earlier years; the pattern does not appear to change significantly from the 1990s.

### Spearman Correlation by Decade for Male Names

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
Decade_Corr_Plot(decade_corr, "M")
```

Once again, this graph shows similar trends to the yearly popular make names graph above. From this graph, it appears that male names are less persistent since the 1990s than prior to that - popular names have become a bit slower to persist since the 1990s.


## Names Surge

The table below shows the top 10 female names and top 10 male names that experienced the largest year-to-year percentage rank improvement. The table excludes names with an initial count of less than 100, so that the rank improvement is not driven by relative large changes in very unpopular names. 

```{r, echo=FALSE}
name_surges <- Yr_on_yr_Surges(baby_names_national)
```

```{r}
Top_Surges_Table(name_surges)
```

## Names Surge and TV Shows/ Movies

```{r, echo=FALSE}
credits_with_titles <-
  Merge_Credits_Titles(
    credits = hbo_credits,
    titles = hbo_titles
  )
```


```{r, echo=FALSE}
matched_characters <-
  Match_Top_Surge_Characters(
    credits = credits_with_titles,
    df_names = baby_names_national,
    top_n = 25
  )
```


```{r, echo=FALSE}
name_media_plots <-
  Name_Media_Spike_Plots_Separate(
    df_names = baby_names_national,
    matched_characters = matched_characters,
    top_n = 25,
    time_unit = "year",
    max_year = 2014
  )
```


### Male Names

The plot below shows how the popularity and persistence of male names interacts with character names of TV show or movie characters. The male names chosen are the 20 male names that experienced the largest percentage rank improvement. These names were then merged with character names.

```{r, echo=FALSE, fig.width=12, fig.height=12, out.width="100%"}
name_media_plots$M
```

As seen from the plot above, there is not a clear pattern between the popularity or persistence of names and character names from TV shows/ movies for these particular male names. However, it is interesting to observe how these variables develop and interact over time. Also, for most of these names, their popularity has been increasing over time. This makes them an excellent choice for a toy company, because their popularity is increasing, and increasing regardless of popular character names. It is clear that some names are classics - Christopher, Michael and Ryan remain persistently popular, regardless of whether TV show or movie characters have these names. These names are also the names of characters in many TV shows/ movies. Therefore, for a toy company, these names are good to take note of, because they are unlikely to change significantly in popularity over time, meaning they are a lower-risk investment.


### Female Names

The plot below shows how the popularity and persistence of female names interacts with character names of TV show or movie characters. The female names chosen are the 20 female names that experienced the largest percentage rank improvement. These names were then merged with character names.

```{r, echo=FALSE, fig.width=12, fig.height=12, out.width="100%"}
name_media_plots$F
```

As seen from the plot above, there is not a clear pattern between the popularity or persistence of names and character names from TV shows/ movies for these particular female names. However, it is interesting to observe how these variables develop and interact over time. It is clear that some names are classics - Michelle, Kayla, Ashley, Jenna and Jamie remain persistently popular, regardless of whether TV show or movie characters have these names. Therefore, for a toy company, these names are good to take note of, because they are unlikely to change significantly in popularity over time, meaning they are a lower-risk investment.
