---
title: "Coffee Supply Analysis"
author: "Anya Nash"
date: "`r Sys.Date()`"
output: powerpoint_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

# loading necessary libraries
library(tidyverse)
library(here)
library(flextable)

```


```{r, include=FALSE}
# loading/ listing all the functions used
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

df_clean <- Data_Loading(Datroot = here("data", "Coffee", "Coffee.csv"))
head(df_clean)

```


## 
```{r, echo=FALSE, fig.width=10, fig.height=5.6, out.width="100%"}
library(ggplot2)

ggplot() +
  annotate("text",
           x = 0.5,
           y = 0.57,
           label = "Some Summary Statistics",
           size = 16,
           fontface = "bold",
           colour = "#61223B") +
  annotate("text",
           x = 0.5,
           y = 0.43,
           label = "A brief overview",
           size = 10,
           colour = "grey35") +
  xlim(0, 1) +
  ylim(0, 1) +
  theme_void()
```

## Average Cost Per 100g by Roast Type

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average price by roast
Average_Barplot(df_clean, Metric = "Cost_Per_100g", Group = "roast")
```

## Average Rating by Roast Type

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average rating by roast
Average_Barplot(df_clean, Metric = "rating", Group = "roast")
```

## Average Cost Per 100g by Country

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average cost by country
Average_Barplot(df_clean, Metric = "Cost_Per_100g", Group = "loc_country")
```

## Average Rating by Country

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average rating by country
Average_Barplot(df_clean, Metric = "rating", Group = "loc_country")
```


## Number of Roasters by Roast Type

```{r, echo=FALSE}
Roasters_Per_Roast_Table(df_clean) %>%
  rename(
    `Roast` = roast,
    `No_of_Roasters` = Number_of_roasters
  ) %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#61223b") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8) %>% 
  set_table_properties(align = "center")
```


## Cost and Rating of Coffee Roasts

```{r, fig.width=12, fig.height=6, out.width="100%"}
Cost_Rating_Scatter(
  df = df_clean,
  Title = "Cost and Rating of Coffee Roasts",
  Subtitle = "Each point represents a coffee, coloured by roast category"
)

```

## 
```{r, echo=FALSE, fig.width=10, fig.height=5.6, out.width="100%"}
library(ggplot2)

ggplot() +
  annotate("text",
           x = 0.5,
           y = 0.57,
           label = "Which Are the Best Coffees?",
           size = 16,
           fontface = "bold",
           colour = "#61223B") +
  annotate("text",
           x = 0.5,
           y = 0.43,
           label = "Identifying the best coffees using various methods",
           size = 10,
           colour = "grey35") +
  xlim(0, 1) +
  ylim(0, 1) +
  theme_void()
```


## Cheapest Roast by Roast Type

```{r, echo=FALSE}
Coffee_Table_By_Roast(df_clean, Choice = "cheapest") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#61223b") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 8) %>% 
  set_table_properties(align = "center")
```

## Highest Rated Roast by Roast Type

```{r, echo=FALSE}
Coffee_Table_By_Roast(df_clean, Choice = "highest_rating") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#61223b") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 8) %>% 
  set_table_properties(align = "center")
```


## Best Valued Roast by Roast Type

```{r, echo=FALSE}
Coffee_Table_By_Roast(df_clean, Choice = "best_value") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#61223b") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 8) %>% 
  set_table_properties(align = "center")
```


## Best Valued Combination for Each Three-Roast Combination

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Coffee_Table_Three_Roast_Combos(df_clean, top_n_per_roast = 10) %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#61223b") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 8)%>% 
  set_table_properties(align = "center")

```


## Best Valued Combination for Each Same-Country Three-Roast Combination

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
  Coffee_Table_Three_Roast_Combos_Same_Country(df_clean) %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#61223b") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 8) %>% 
  set_table_properties(align = "center")
```

## 
```{r, echo=FALSE, fig.width=10, fig.height=5.6, out.width="100%"}
library(ggplot2)

ggplot() +
  annotate("text",
           x = 0.5,
           y = 0.57,
           label = "Recommendations",
           size = 16,
           fontface = "bold",
           colour = "#61223B") +
  annotate("text",
           x = 0.5,
           y = 0.43,
           label = "Best coffees to stock",
           size = 10,
           colour = "grey35") +
  xlim(0, 1) +
  ylim(0, 1) +
  theme_void()
```

## Recommendation 1

If just one type of coffee is to be stocked, I would recommend this coffee:

- Medium-Light roast: Karen J Kona Red Bourbon, roasted by Hula Daddy Kona Coffee
- It has the best value for money
- It is both inexpensive and highly rated

## Recommendation 2

If the goal is to supply a range of coffee roasts, I would recommend the following combination:

- A medium roast: Espresso Blend
- A medium-dark roast: 100% Guatemalan
- And a medium-light roast: Karen J Kona Red Bourbon

## Recommendation 3

If the goal is to supply a range of coffee roasts and there is an advantage from importing them all from the same country, I would recommend the following roasts from Hawai'i:

- Light roast: Ethiopia Yirgacheffe G1
- Medium roast: Medium-Dark Roast
- And medium-light roast: Karen J Kona Red Bourbon





