---
title: "Coffee"
author: "Anya Nash"
date: "`r Sys.Date()`"
output:
  officedown::rpptx_document:
    layout: "Title and Content"
    master: "Office Theme"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

# loading necessary libraries
library(tidyverse)
library(here)
library(flextable)
library(officedown)

```


```{r, include=FALSE}
# loading/ listing all the functions used
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

df_clean <- Data_Loading(Datroot = here("data", "Coffee", "Coffee.csv"))
head(df_clean)

```


# Average Cost Per 100g by Roast Type

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average price by roast
Average_Barplot(df_clean, Metric = "Cost_Per_100g", Group = "roast")
```

# Average Rating by Roast Type

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average rating by roast
Average_Barplot(df_clean, Metric = "rating", Group = "roast")
```

# Average Cost Per 100g by Country

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average cost by country
Average_Barplot(df_clean, Metric = "Cost_Per_100g", Group = "loc_country")
```

# Average Rating by Country

```{r, fig.width=12, fig.height=6, out.width="100%"}
# Average rating by country
Average_Barplot(df_clean, Metric = "rating", Group = "loc_country")
```


# Number of Roasters by Roast Type

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Roasters_Per_Roast_Table(df_clean) %>%
  rename(
    `Roast` = roast,
    `No_of_Roasters` = Number_of_roasters
  ) %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)
```


# Cost and Rating of Coffee Roasts

```{r, fig.width=12, fig.height=6, out.width="100%"}
Cost_Rating_Scatter(
  df = df_clean,
  Title = "Cost and Rating of Coffee Roasts",
  Subtitle = "Each point represents a coffee, coloured by roast category"
)

```



# Cheapest Roast by Roast Type

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Coffee_Table_By_Roast(df_clean, Choice = "cheapest") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)
```

# Highest Rated Roast by Roast Type

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Coffee_Table_By_Roast(df_clean, Choice = "highest_rating") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)
```


# Best Valued Roast by Roast Type

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Coffee_Table_By_Roast(df_clean, Choice = "best_value") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)
```


# Best Valued Roast by Roast Type in Africa

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Coffee_Table_By_Roast(df_clean, Choice = "Africa_best_value") %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)
```

# Best Valued Combination for Each Three-Roast Combination

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
Coffee_Table_Three_Roast_Combos(df_clean, top_n_per_roast = 10) %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)

```


# Best Valued Combination for Each Same-Country Three-Roast Combination

```{r, echo=FALSE, ph = officer::ph_location(left = 0, width = 10.8)}
  Coffee_Table_Three_Roast_Combos_Same_Country(df_clean) %>%
  flextable() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#4D0E31") %>%
  color(part = "header", color = "white") %>%
  fontsize(size = 14, part = "all") %>%
  autofit() %>%
  fit_to_width(max_width = 10.8)
```

