---
# IMPORTANT: Change settings here, but DO NOT change the spacing AT ALL.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Loans and Credit"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

Thesis_FP: FALSE

AddTitle: TRUE 
Author1: "Anya Nash"  
Ref1: "Stellenbosch University, Stellenbosch, South Africa" 
Email1: "25051911\\@sun.ac.za" 
CorrespAuthor_1: TRUE  

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- General:
RemovePreprintSubmittedTo: FALSE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

library(tidyverse)
library(here)

```

```{r, echo=FALSE}
# load code scripts
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

```{r, echo=FALSE}
# load data 
loans_clean <- Data_Clean(
  df = readRDS(here::here("data", "Loan_Cred", "loan_data.rds"))
)
```

## Default Profile Summary Statistics

### Default Rate by Grade

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
default_by(loans_clean, grade)
```

It is clear from the graph that as credit grade goes from A to G, the default rate increases exponentially. Therefore, grade is highly associated with the default rate (although that is how it is designed).

### Default Rate by Term of Loan

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
default_by(loans_clean, term)
```

There is a small difference in the default rate based on the length of the loan, with the longer loan having a slightly higher default rate.

### Default Rate by Length of Employment

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
default_by(loans_clean, emp_length)
```

There is not a substantial difference in the default rate based on the length of employment, except for those who have n/a for length of employment - they have a much higher default rate. This is logical, because those who answered n/a to length of employment are most likely not working/ unemployed. Thus, they probably have a less stable income, which would make their default rate higher.

### Default Rate by State

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
default_by(loans_clean, addr_state)
```

There is no obvious outlier in the default rate based on US state, however, the difference in default rate between the state with the highest default rate (Alabama) and the state with the lowest default rate (West Virginia) is substantial. Texas has a default rate on the higher side, however, it is not obviously different from any of the other states.

### Default Rate by State for Short Term Loans

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
loans_clean_sr <- loans_clean %>% 
  filter(str_trim(term) == "36 months")
default_by(loans_clean_sr, addr_state)
```

There is no obvious outlier in the default rate based on US state for short term loans, however, the difference in default rate between the state with the highest default rate (Alabama) and the state with the lowest default rate (West Virginia) is substantial. Texas has a default rate on the higher side, however, it is not obviously different from any of the other states.

### Default Rate by DTI Band

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
default_by(loans_clean, dti_band)
```

The default rate for different bands of the debt-to-income ratio follows an expected pattern. The default rate is lower for a lower debt-to-income ratio, and the default rate is higher for a higher debt-to-income ratio. 

### Default Rate by Purpose of Loan

```{r, echo=FALSE, fig.width=12, fig.height=6, out.width="100%"}
default_by(loans_clean, purpose)
```

The default rate differs a bit based on the purpose of the loan. Loans for paying off credit cards or buying cars have the lowest default rate, while loans for weddings and small businesses have the highest default rate. It is logical that loans for small businesses have the highest default rate, since small businesses often carry a higher investment risk, and have unpredictable profits (and often low/ no initial profits). 


## Default Rate, Credit Grades and Young Individuals

Unfortunately, there is no age variable in the data. Therefore, as a very rough, imperfect proxy for age, I use length of employment. I classify young individuals as those with a length of employment of 5 years or less. Then, to determine whether credit grades are a good indicator for whether younger individuals will default on their loans, I regress the default rate on credit grade, restricting the sample to younger individuals only. The table below shows the results of the regression.

```{r, echo=FALSE, include=FALSE}
model <- loans_clean %>%
  filter(emp_length %in% c("< 1 year", "1 year", "2 years", "3 years", "4 years", "5 years")) %>%
  lm(default ~ factor(grade), data = .)

summary(model)
```

```{r, echo=FALSE}
Model_Table(model)
```


As seen in the regression table above, credit grade is a somewhat good indicator of whether younger individuals will default. This is because all the coefficients are statistically significant with an economically-meaningful magnitude, however, the R-squared value is quite low at 0.04928, meaning there are many other factors that influence the default rate of young individuals.


## Interest Rates, Age, Occupation and Credit Scores


```{r, echo=FALSE, include=FALSE,fig.width=12, fig.height=6, out.width="100%"}
loans_clean <- loans_clean %>%
  Create_Job_Groups()
```

Using employment length as an imperfect, rough proxy for age once again and using very rough occupation categories, I regress interest rate on employment length, occupation and credit score to determine whether interest rates are determined by these factors. The results are displayed below.

```{r, echo=FALSE, include=FALSE}
library(fixest)

model_2 <- feols(
  int_rate ~ 1 | grade + emp_length + emp_title_clean,
  data = loans_clean
)

summary(model_2)
```

```{r, echo=FALSE}
summary(model_2)
```
With an R-squared value of 0.926009, it is clear that interest rates are strongly associated with age, occupation and credit scores.


## Risk Profiles

The table below shows the top 10 combinations of credit grade, DTI band, purpose of loan and type of home ownership that have the highest default rates. 

```{r, echo=FALSE}
Risk_Profiles_df(loans_clean)
```

From the table above, we can see that the highest defaulters are individuals with credit grades of either F or G, a DTI that is greater than 25 and who rent their homes. The median income for each group is between 50000 and 60000 US dollars.

When lenders assess borrower credibility, they can do a number of things to reduce default risk. They can identify those borrowers who are part of the highest default risk combination categories and either reduce the loan amount to these borrowers, or have additional checks and balances before approving the loan. Instead of just focusing on one category or "tick-box" at a time, lenders now have a better, fuller picture of the default risk of the borrower. A borderline answer for one or two categories could be viewed as okay when each category is viewed in isolation, but could paint a much riskier picture when categories are viewed together.

## DTI Cap

The table below shows how the share of loans accepted and default rate would change, if there was a DTI cap imposed.

```{r, echo=FALSE}
DTI_Cap_Table(loans_clean)
```

As seen in the table above, as the DTI cap increases, both the share accepted and default rate increase. Therefore, there is a trade-off between the risk of default and maximising the number of borrowers. A DTI cap that is too strict will cause the number of borrowers to decline significantly, however, it would also have the positive effect of reducing the default rate. The same goes for a DTI cap that is too lenient - the number of borrowers will increase, but at the cost of the default rate increasing as well. I think an appropriate hard-cap for DTI levels is 25. At 25, approximately 75% of borrowers are accepted, which is not too low, and the default rate is at 9%, which is an improvement compared to no DTI cap.

